Presentation Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-02-23 presentation-plan/presentation-plan.tex
Spelling typos

FF-Replan is an action selection algorithm for online planning in probabilistic domains. Given a domain description, a goal and an initial state as a probabilistic planning problem, FF-Replan generates a deterministic planning problem. It determinizes the input domain at the start of the planning into a deterministic different domain. They consider two methods of determinization:
\begin{enumerate}
	\item \emph{Single-outcome determinization}: selects one outcome for each probabilistic construct using a variety of heuristics. The performance strongly depends on the methods for choosing the outcomes.
	\item \emph{All-outcomes determinization}: considers every probabilistic outcome as a distinct deterministic action. For each possible outcome  FF-Replan generates one seperate action for each effect. For nested probabilities, the all-outcomes procedure is applied recursively. This implies that FF-Replan will ceise selecting actions whenever it enters a dead state. However when given no information, all probabilistic effects will be considered as equal which is a potential weakness.
\end{enumerate}

After determinization FF-Replan then uses the deterministic FF planner to compute an ordered plan for the generated deterministic problem. This process is repeated when countering an unexpected state untill a goal state is reached. It maintains a partial state-action mapping using a hash-table which is initially empty. Whenever FF-Replan encounters a state which is not in the table, it determinizes the problem and synthesizes a plan using FF. It then simulates the plan according to the deterministic action definitions resulting in a state-action sequence whose pairs are put in the hash table. The first action of the plan is then executed in the environment, returning a new state. This partial policy is this produces in an online fashion. It would be valuable to look into incremental planning approaches that don't create a deterministic plan from scratch whenever an unexpected state is encountered or reusing previous planning effort.

>>>>

FF-Replan is an action selection algorithm for online planning in probabilistic domains. Given a domain description, a goal and an initial state as a probabilistic planning problem, FF-Replan generates a deterministic planning problem. It determinizes the input domain at the start of the planning into a deterministic different domain. They consider two methods of determinization:
\begin{enumerate}
	\item \emph{Single-outcome determinization}: selects one outcome for each probabilistic construct using a variety of heuristics. The performance strongly depends on the methods for choosing the outcomes.
	\item \emph{All-outcomes determinization}: considers every probabilistic outcome as a distinct deterministic action. For each possible outcome  FF-Replan generates one seperate action for each effect. For nested probabilities, the all-outcomes procedure is applied recursively. This implies that FF-Replan will cease selecting actions whenever it enters a dead state. However when given no information, all probabilistic effects will be considered as equal which is a potential weakness.
\end{enumerate}

After determinization FF-Replan then uses the deterministic FF planner to compute an ordered plan for the generated deterministic problem. This process is repeated when countering an unexpected state until a goal state is reached. It maintains a partial state-action mapping using a hash-table which is initially empty. Whenever FF-Replan encounters a state which is not in the table, it determinizes the problem and synthesizes a plan using FF. It then simulates the plan according to the deterministic action definitions resulting in a state-action sequence whose pairs are put in the hash table. The first action of the plan is then executed in the environment, returning a new state. This partial policy is this produces in an online fashion. It would be valuable to look into incremental planning approaches that don't create a deterministic plan from scratch whenever an unexpected state is encountered or reusing previous planning effort.
